### 2021-06-28 notes/notes.tex
Updated timetable.tex with new timings

\begin{tabularx}{\textwidth}{
  l|
  >{\hsize=0.4\hsize\linewidth=\hsize}X|
  >{\hsize=0.2\hsize\linewidth=\hsize}X|
  >{\hsize=0.2\hsize\linewidth=\hsize}X}
End Date & Result & A priori comments & A posteriori comments \\ \hline \hline
30.04.2021 & Lit. research on savings and deadaptation & Are there many with contextual cues? & I found a lot of evidence. Moving on.\\ \hline
07.05.2021 & Finding model pars to explain observations & This is mostly already done &  \\\hline
14.05.2021 & Looking into error-clamp behavior & Maybe there's something to it. If there is, an extra week should be allocated to simulations. &  \\\hline
--- & Start writing the paper. & & \\ \hline

@@

\section{Results}

\begin{enumerate}
\item Quick de-adaptation/savings: gradual evidence accumulation during context inference will make the switching between internal models not be immediate.
\item Learning: The speed in which the internal models are adjusted given errors depends on how certain the inference is. More uncertain context inference will lead to slower learning.
\item Action selection: Action selection is sampled from the existing (relevant) internal models, weighted by their posterior probability during this trial.
\item Cue reliability adjustments: As more bad-cue trials are observed, the agent will lower the estimated reliability of the cue.
\item Error-clamp tappering off: Hundreds of error-clamp trials make adaptation seem to slowly disappear, but it never fully goes away.
\item Error-clamp lag: For a while, the tappering off does not begin, depending on how clear it is that error-clamp trials have started.
\end{enumerate}

>>>>

\begin{tabularx}{\textwidth}{
  l|
  >{\hsize=0.4\hsize\linewidth=\hsize}X|
  >{\hsize=0.2\hsize\linewidth=\hsize}X|
  >{\hsize=0.2\hsize\linewidth=\hsize}X}
End Date & Result & A priori comments & A posteriori comments \\ \hline \hline
30.04.2021 & Lit. research on savings and deadaptation & Are there many with contextual cues? & I found a lot of evidence. Moving on.\\ \hline
07.05.2021 & Finding model pars to explain observations & This is mostly already done &  Parameters found\\\hline
14.05.2021 & Looking into error-clamp behavior & Maybe there's something to it. If there is, an extra week should be allocated to simulations. & I found a lot of evidence for context-inference-based motor adaptation. It will be incorporated into the paper. \\\hline
23.06.2021 & Looking into single-cell recordings. & Perhaps I can find evidence here. & Evidence seems dubiuous, but might be worth including in Discussion \\
--- & Start writing the paper. & & This was delayed by the defense and dysco. Restarted around 24.06.2021 \\ \hline

@@

\section{Results}
Possible results to include in the paper:
\begin{enumerate}
\item Quick de-adaptation/savings: gradual evidence accumulation during context inference will make the switching between internal models not be immediate.
\item Learning: The speed in which the internal models are adjusted given errors depends on how certain the inference is. More uncertain context inference will lead to slower learning.
\item Action selection: Action selection is sampled from the existing (relevant) internal models, weighted by their posterior probability during this trial.
\item Cue reliability adjustments: As more bad-cue trials are observed, the agent will lower the estimated reliability of the cue.
\item Error-clamp tappering off: Hundreds of error-clamp trials make adaptation seem to slowly disappear, but it never fully goes away.
\item Error-clamp lag: For a while, the tappering off does not begin, depending on how clear it is that error-clamp trials have started.
\end{enumerate}

### 2021-06-28 timetable.tex
Updated timetable.tex with new timings

\begin{document}
\section*{Brief project description}
In this chapter, I describe the everything related to the paper that should come
out of this project, including modeling and experimental findings, as well as
the direction of the paper and things needed to get there.

@@

\begin{tabularx}{\textwidth}{
  l|
  >{\hsize=0.4\hsize\linewidth=\hsize}X|
  >{\hsize=0.2\hsize\linewidth=\hsize}X|
  >{\hsize=0.2\hsize\linewidth=\hsize}X}
End Date & Result & A priori comments & A posteriori comments \\ \hline \hline
30.04.2021 & Lit. research on savings and deadaptation & Are there many with contextual cues? & I found a lot of evidence. Moving on.\\ \hline
07.05.2021 & Finding model pars to explain observations & This is mostly already done &  \\\hline
14.05.2021 & Looking into error-clamp behavior & Maybe there's something to it. If there is, an extra week should be allocated to simulations. &  \\\hline
--- & Start writing the paper. & & \\ \hline

\end{tabularx}
\section{Results}

\begin{enumerate}
\item Quick de-adaptation/savings: gradual evidence accumulation during context inference will make the switching between internal models not be immediate.
\item Learning: The speed in which the internal models are adjusted given errors depends on how certain the inference is. More uncertain context inference will lead to slower learning.
\item Action selection: Action selection is sampled from the existing (relevant) internal models, weighted by their posterior probability during this trial.
\item Cue reliability adjustments: As more bad-cue trials are observed, the agent will lower the estimated reliability of the cue.
\item Error-clamp tappering off: Hundreds of error-clamp trials make adaptation seem to slowly disappear, but it never fully goes away.
\item Error-clamp lag: For a while, the tappering off does not begin, depending on how clear it is that error-clamp trials have started.
\end{enumerate}

>>>>

\begin{document}
In this chapter, I describe the everything related to the paper that should come
out of this project, including modeling and experimental findings, as well as
the direction of the paper and things needed to get there.

@@

\begin{tabularx}{\textwidth}{
  l|
  >{\hsize=0.4\hsize\linewidth=\hsize}X|
  >{\hsize=0.2\hsize\linewidth=\hsize}X|
  >{\hsize=0.2\hsize\linewidth=\hsize}X}
End Date & Result & A priori comments & A posteriori comments \\ \hline \hline
30.04.2021 & Lit. research on savings and deadaptation & Are there many with contextual cues? & I found a lot of evidence. Moving on.\\ \hline
07.05.2021 & Finding model pars to explain observations & This is mostly already done &  Parameters found\\\hline
14.05.2021 & Looking into error-clamp behavior & Maybe there's something to it. If there is, an extra week should be allocated to simulations. & I found a lot of evidence for context-inference-based motor adaptation. It will be incorporated into the paper. \\\hline
23.06.2021 & Looking into single-cell recordings. & Perhaps I can find evidence here. & Evidence seems dubiuous, but might be worth including in Discussion \\ \hline
--- & Start writing the paper. & & This was delayed by the defense and dysco. Restarted around 24.06.2021 \\ \hline

\section{Results}
Possible results to include in the paper:
\begin{enumerate}
\item Quick de-adaptation/savings: gradual evidence accumulation during context inference will make the switching between internal models not be immediate.
\item Learning: The speed in which the internal models are adjusted given errors depends on how certain the inference is. More uncertain context inference will lead to slower learning.
\item Action selection: Action selection is sampled from the existing (relevant) internal models, weighted by their posterior probability during this trial.
\item Cue reliability adjustments: As more bad-cue trials are observed, the agent will lower the estimated reliability of the cue.
\item Error-clamp tappering off: Hundreds of error-clamp trials make adaptation seem to slowly disappear, but it never fully goes away.
\item Error-clamp lag: For a while, the tappering off does not begin, depending on how clear it is that error-clamp trials have started.
\end{enumerate}
